A Switching Planner for Combined Task and Observation Planning

### 2010-11-28 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
More work on evaluation. Converted plots to pdf.

The basic building blocks of the domain consist of {\tt rooms}, {\tt
places} and {\tt objects}. Places are grouped in rooms and objects (as
well as the robot) are always in a place. The robot can move around
the rooms via connections between places given by the {\tt connected}
predicate. Each room has a (possibly unknown) {\em category/}
(e.g. kitchen, office, living room) and depending on this category,
objects are placed inside the rooms. An instance of this domain is
shown in figure\ref{fig}.

@@

We conducted experiments on scenarios of several sizes with several
kinds of goals (though the goal is always reporting the position of a
certain kind of object). In order to determine the impact of sensor
reliability on both approaches, we also ran several tests in identical
problems with different probabilities for sensing the goal object. The
perception probabilities were 0.9, 9.65 and 04. As the initial state
of the problems is stochastic, we ran 50 simulations for each
configuration. The samples for the true initial state were drawn from
the same distribution that was used for planning, so the planner's
model matched its simulated world exactly. Not all problems generated
in this manner have a solution. We did not reject these problems, as
we believe that detecting the non-existance of a solution is as valuable
in exploration problems than finding one.

@@

\begin{figure}[h!]
  \centering
  \includegraphics{dora1-time}
  \includegraphics{dora2-time}
  \includegraphics{dora3-time}
  \includegraphics{dora4-time}
  \includegraphics{dora56-time}
  \caption{Average runtime}
  \label{fig:results-time}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics{dora1-quality}
  \includegraphics{dora2-quality}
  \includegraphics{dora3-quality}
  \includegraphics{dora4-quality}
  \includegraphics{dora56-quality}
  \caption{Average plan costs and number of successful runs}
  \label{fig:results-quality}
\end{figure}

The graphs in figure \ref{fig:results-time} show the average planning
times. For the smaller belief states, the cost for the decision
theoretic planning is compensated by the decrease of time spent in
Fast Downward.

@@

Impact of state space size: the configuration with a belief space size
of 200 was noticably slower than the other configurations while having
no noticable benefit.

We believe that a part of the improvement is due to the segmentation of
the plan into several subtask, essentially performing hierarchical
planning. Especially when the continual planner performs badly this is
a huge gain.

>>>>

\begin{figure}[h]
  \centering
  \input{figures/dora}
  \caption{A exploration domain with three rooms and 13 places. The
    robot is in in the center of room A}
\label{fig:dora2}
\end{figure}
An instance of this domain is shown in figure \ref{fig:dora2}. The
basic building blocks of the domain consist of {\tt rooms}, {\tt
  places} and {\tt objects}. Places are grouped in rooms and objects
(as well as the robot) are always in a place. The robot can move
around the rooms via connections between places given by the {\tt
  connected} predicate. Each room has a (possibly unknown) {\em
  category/} (e.g. kitchen, office, living room) and depending on this
category, objects are placed inside the rooms.

@@

We conducted experiments on scenarios of several sizes. The robot's
goal was to find one or more objects and report back their position to
a person. In order to determine the impact of sensor reliability on
both approaches, we also ran tests on identical problems but changed
the sensor model for the goal objects: the probability for percieving
the object if it was there went from 0.9 in the easiest case to 0.65
and 0.4 in the average and hard cases. In addition, we wanted to test
how our system performed on tasks requiring indirect sensing, so we
gave the planner goals to visit a certain type of room (e.g. kitchen
or office). We didn't place any humans in those scenarios, so the only
way of determining the room category was by looking for objects
typical for that room type. As this indirect reasoning is a tasks that
cannot be performed by the continual planner alone, we did not run the
baseline system on those problems.

As the initial state of the problems is stochastic, we ran 50
simulations for each configuration. The samples for the true initial
state were drawn from the same distribution that was used for
planning, so the planner's model matched its simulated world
exactly. Not all problems generated in this manner have a solution. We
did not reject these problems, as we believe that detecting the
non-existance of a solution is important in stochastic domains.

@@

Using a satisficing, optimistic serial planner and using continual
planning makes optimising for the expected reward difficult. The
continual planner will in general be overly optimistic regarding the
remaining costs to the goal while being overly pessimistic regarding
the probability of reaching it (as it only regards one trace). This
means that setting the reward function to non-extremal setting had
little effect on the resulting planner behaviour. For this reason, we
chose not to use the expected reward as a metric for our results, as
that information would have been of little value to the
reader. Instead we show the average costs of the plan and the success
rate (as a ratio between solved and solvable problems) separately.

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-time}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-time}\hfill
  \vspace{2mm}
  \includegraphics{dora3-time}\hfill
  \vspace{2mm}
  \includegraphics{dora4-time}\hfill
  \vspace{2mm}
  \includegraphics{dora56-time}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-time}\hfill
  \caption{Average runtime}
  \label{fig:results-time}
\end{figure}

\begin{figure}[h!]
  % \centering
  % \includegraphics{dora1-quality}\hfill
  % \vspace{2mm}
  \includegraphics{dora2-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora3-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora4-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora56-quality}\hfill
  \vspace{2mm}
  \includegraphics{dora-cat-quality}\hfill
  \caption{Average plan costs and number of successful runs}
  \label{fig:results-quality}
\end{figure}

The graphs in figure \ref{fig:results-time} show the average planning
times. Not surprisingly, the time the POMDP planner takes increases
strongly with larger belief spaces. But for the smaller belief states,
the cost for the decision theoretic planning is compensated by the
decrease of time spent in Fast Downward.

@@

As already mentioned, less aggressive pruning of the initial belief
space resultes in longer runtimes. The impace of the pruning on plan
costs and success rate were limited, though. Increasing the size limit
beyond 50 did rarely pay off because while additional information
might in theroy allow better plans, (add reason here). The indirect
sensing tests show the same result, though with much higher time spent
in the decision theoretic planner. The relatively high success rate
even with small belief spaces might also indicate that the entropy
heuristic for belief space pruning is effective in keeping the most
relevant information.

% We believe that a part of the improvement is due to the segmentation of
% the plan into several subtask, essentially performing hierarchical
% planning. Especially when the continual planner performs badly this is
% a huge gain.
